---
title: "`r params$title`"
date: "`r format(Sys.time(), '%d %B, %Y')`" 
output: html_document
params:
  title: BRINDA Adjustment Report
  data: NULL
  plot: NULL
  rbp: NULL
  rt: NULL
  ft: NULL
  stfr: NULL
  zn: NULL
  agp: NULL
  crp: NULL
  pop: NULL
  rbpC: NULL
  rtC: NULL
  ftC: NULL
  stfrC: NULL
  znC: NULL
  rbpPlotCf: NULL
  rtPlotCf: NULL
  ftPlotCf: NULL
  stfrPlotCf: NULL
  znPlotCf: NULL
  refAgp : NULL
  refCrp :  NULL
  bar : NULL
  density : NULL
---

## Input Data

The input data has `r nrow(params$data)` samples and `r ncol(params$data)` observations per sample. The following micronutrients were assigned to the column names listed below:

| Micronutrient | Assigned Column Name |
|-|-|
| Retinol Binding Protein| `r params$rbp` |
| Retinol | `r params$rt` |
| Ferritin | `r params$ft` |
| Soluble Transferrin Receptor | `r params$stfr` |
| Serum Zinc | `r params$zn` |
| AGP | `r params$agp` |
| CRP | `r params$crp` |                                          

## Value Cutoffs

The following cutoff was applied to the micronutrients below. Micronutrients with a level below the cutoff were not adjusted using the BRINDA method:

| Micronutrient | Value Cutoff |
|-|-|
| Retinol Binding Protein| `r params$rbpC` |
| Retinol | `r params$rtC` |
| Ferritin | `r params$ftC` |
| Soluble Transferrin Receptor | `r params$stfrC` |
| Serum Zinc | `r params$znC` |


```{r cutoff,echo=FALSE,warning=F,message=FALSE}
library(patchwork)
library(ggplot2)
(params$rbpPlotCf / params$rtPlotCf / params$ftPlotCf) | ( params$stfrPlotCf / params$znPlotCf /ggplot() + theme_void())
```

## Population Group

Micronutrient values are adjusted per population group and as such reference AGP and CRP values are set accordingly. The population group, reference AGP, and reference CRP were set to the following:

```{r population,echo=FALSE,warning=F,message=FALSE}
population = params$pop
if(population == "PSC"){
  refAgp = "-0.52"
  refCrp = "-2.26"
}else if(population == "WRA"){
  refAgp = "-0.62"
  refCrp = "-1.83"
}else if(population == "Manual"){
  refAgp = "lowest decile of AGP"
  refCrp = "lowest decile of CRP"
}else if(population == "Other"){
  refAgp = params$refAgp
  refCrp = params$refCrp
}
```

* Population : `r population`
* Reference AGP : `r refAgp`
* Reference CRP : `r refCrp`

## BRINDA Adjustment

The micronutrient values have been adjusted and the difference between adjusted and unadjusted values are displayed below:

```{r adjustment,echo=FALSE,warning=F,message=FALSE}
library(patchwork)
params$bar/params$density
```
